United Monoids

### 2022-01-11 paper/main.tex
Tweaks for camera-ready version

\documentclass[english,submission]{programming}
\usepackage[backend=biber]{biblatex}
\addbibresource{refs.bib}
\usepackage{svg}
\svgpath{img}

@@

\begin{document}

@@

\title{United Monoids}
\subtitle{Finding Simplicial Sets and Labelled Algebraic Graphs in Trees}
\author[~]{Andrey Mokhov}
\affiliation[~]{\hspace{-5.3mm}Jane Street, London, UK}
\affiliation[~]{\hspace{-5.3mm}Newcastle University, Newcastle upon Tyne, UK}

@@

\section{Simplicial sets}\label{sec-simplicial-set}
\vspace{-1mm}

@@

\subsection{Other kinds of graphs}\label{sec-other-graphs}

@@

\section{Preorders and generalised transitively-closed graphs}\label{sec-preorder}

@@

\subsection{Acyclic graphs and partial orders}\label{sec-acyclic-graphs}
\vspace{-1mm}

@@

\section{Edge-labelled graphs}\label{sec-labelled}

@@

\subsection{From $0=1$ to containment laws and back}

@@

\subsection{Examples from this paper}

@@

\subsection{Other examples}

@@

% Naturally ordered
% Use trees/united monoids for modelling parallel/sequential composition
% What about tries?
% Equivalence classes?
% Languages

\section{Related work}\label{sec-related-work}

@@

\section*{Acknowledgements}
Many people contributed to this research by giving feedback on earlier versions
of this work, participating in numerous online and in-person discussions, and
last but not least, expressing genuine interest and encouragement.

Here is a most likely incomplete list (I apologise for any omissions):
Arseniy Alekseyev, Roland Backhouse, Gershom Bazerman,
Dave Clarke, Ulan Degenbaev, Chris Doran, Victor Khomenko, Adithya Kumar,
Dave Long, Anton Lorenzen, Georgy Lukyanov, Alp Mestanogullari, Alexandre Moine,
Andreas Nuyts, Greg Pfeil, Stefan Plantikow, Armando Santos, Danil Sokolov,
Sjoerd Visscher, Leo White and Alex Yakovlev. I am also grateful to the the
Programming Journal's Programme Committee for the thorough reviews that helped
me improve the final version of the paper.

\printbibliography
\end{document}

>>>>

\documentclass[crc,english]{programming}
\usepackage[backend=biber]{biblatex}
\addbibresource{refs.bib}
\usepackage{svg}
\svgpath{img}

@@

%%% The following is specific to Programming Journal, Volume 6, Issue 3 and the paper
%%% 'United Monoids: Finding Simplicial Sets and Labelled Algebraic Graphs in Trees'
%%% by Andrey Mokhov.
%%%
\paperdetails{
  submitted=2021-10-01,
  published=2022-02-15,
  year=2022,
  volume=6,
  issue=3,
  articlenumber=12,
}
\begin{document}

@@

\title{United Monoids}
\subtitle{Finding Simplicial Sets and Labelled Algebraic Graphs in Trees}
\author[~]{Andrey Mokhov}
\authorinfo{is a software engineer at Jane Street London,
  and a visiting fellow at Newcastle University, UK. His
  research interests are in applying abstract mathematics and
  functional programming to solving large-scale engineering
  problems.
  \begin{description}
    \item[email:] \email{andrey.mokhov@ncl.ac.uk}
  \end{description}}
\affiliation[~]{\hspace{-5.3mm}Jane Street, London, UK}
\affiliation[~]{\hspace{-5.3mm}Newcastle University, Newcastle upon Tyne, UK}

@@

\section{Simplicial Sets}\label{sec-simplicial-set}
\vspace{-1mm}

@@

\subsection{Other Kinds of Graphs}\label{sec-other-graphs}

@@

\section{Preorders and Generalised Transitively-Closed Graphs}\label{sec-preorder}

@@

\subsection{Acyclic Graphs and Partial Orders}\label{sec-acyclic-graphs}
\vspace{-1mm}

@@

\section{Edge-Labelled Graphs}\label{sec-labelled}

@@

\subsection{From $0=1$ to Containment Laws and Back}

@@

\subsection{Examples from This Paper}

@@

\subsection{Other Examples}

@@

% Naturally ordered
% What about tries?
% Equivalence classes?
% Languages

\section{Related Work}\label{sec-related-work}

@@

\acks
I would like to thank everyone who contributed to this research by giving
feedback on earlier versions of this work, participating in numerous online and
in-person discussions, and last but not least, expressing genuine interest and
encouragement.
Here is a most likely incomplete list (I apologise for any omissions):
Arseniy Alekseyev, Roland Backhouse, Gershom Bazerman,
Dave Clarke, Ulan Degenbaev, Chris Doran, Victor Khomenko, Adithya Kumar,
Dave Long, Anton Lorenzen, Georgy Lukyanov, Alp Mestanogullari, Alexandre Moine,
Andreas Nuyts, Greg Pfeil, Stefan Plantikow, Armando Santos, Danil Sokolov,
Sjoerd Visscher, Leo White and Alex Yakovlev. I am also grateful to the
Programming Journal's Programme Committee for the thorough reviews that helped
me improve the final version of the paper.

\newpage
\printbibliography
\end{document}
